---
title: "Ranking of articles"
author: "Etienne Rolland"
date: "20/01/2020"
output: 
  html_document :
    toc : true
  # github_document:
  #   toc: true
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(dplyr)
library(readr)
library(stringr)
library(tabulizer)
library(tm)
library(ggplot2)
library(xlsx)
```

## Ranking of the material and method section

Note that the R code used to create the automatic ranking his hidded to make it more easily readable. A version with the code visible is available on the Github repository.

```{r functions}

create_quality_df <- function(material_characterisation) {
  #this function create the dataframe quality_evaluation that store the informations
  #of the quality evalution assessment
  
  #nb_technical_aspect<-length(material_characterisation)
  technical_aspect<-names(material_characterisation)
  names_columns<-c("Article_name", technical_aspect)
  names_columns<-c("Folder_name", technical_aspect)

  
  quality_evaluation_df<-as.data.frame(matrix(ncol=length(names_columns), 
                                              byrow=TRUE))
  
  colnames(quality_evaluation_df)<-names_columns
  
  return(quality_evaluation_df)
}

init_quality_df <- function(quality_evaluation_df, pdf_name, folder_name) {
  #create empty dataframe is such a pain in R
  #initiate the quality_df dataframe, i.e., add zero everywhere and the pdf name,
  #for the first iteration of the loop
  quality_evaluation_df[["Article_name"]]<-pdf_name
  quality_evaluation_df[["Folder_name"]]<-folder_name
  quality_evaluation_df[is.na(quality_evaluation_df)] = 0
  
  return(quality_evaluation_df)
}

is_double_space <- function(word) {
  res<-str_split(word, "\\s")[[1]]
  if (length(res)==3) {
    return(TRUE)
  }
  return(FALSE)
}

is_space <- function(word) {
  res<-str_split(word, "\\s")[[1]]
  if (length(res)==2) {
    return(TRUE)
  }
  return(FALSE)
}

is_not_space <- function(word) {
  res<-str_split(word, "\\s")[[1]]
  if (length(res)==1) {
    return(TRUE)
  }
  return(FALSE)
}

cut_word <- function(word) {
  res<-str_split(word, "\\s")[[1]]
  return(res)
}

attribute_ranking_split_word <- function(x, i, quality_evaluation_df, technical_aspect, word) {
  res<-cut_word(word)
  first_word<-res[1]
  second_word<-res[2]
  idx<-which(x$lemma==first_word) #firstword
  
  if (length(idx)>0) { #if the word is present as lemma
    for (id in idx) {   #if several times the word, simply
      if (x[(id+1),]$lemma==second_word) {
        quality_evaluation_df[i,][[technical_aspect]]<-1
      }
    }
  }
  
  return(quality_evaluation_df)
}

attribute_ranking <- function(x, i, quality_evaluation_df, technical_aspect, word) {
  idx<-which(x$lemma==word)
  if (length(idx)>0) { #if the word is present as lemma
    for (id in idx){
      sentence<-x[id,]$sentence
    }
    quality_evaluation_df[i,][[technical_aspect]]<-1
    # if (word=="size") {
    #   print(x[idx,]$sentence)
    # }
  }
  return(quality_evaluation_df)
}

quality_assessment <- function(x, i, pdf_name, quality_evaluation_df, ontology_material_characterisation, folder_name) {
  if (first_iteration(i)) {
    quality_evaluation_df<-init_quality_df(quality_evaluation_df, pdf_name, folder_name)
  } else {
    quality_evaluation_df<-rbind(quality_evaluation_df, c(0))
    quality_evaluation_df[i,]$Article_name<-pdf_name
    quality_evaluation_df[i,]$Folder_name<-folder_name
  }
  for (technical_aspect in names(ontology_material_characterisation)) { #Size, surface area, etc
    for (word in ontology_material_characterisation[[technical_aspect]]) { #Diameter
      if (is_space(word)) {
        quality_evaluation_df<-attribute_ranking_split_word(x, i, quality_evaluation_df, technical_aspect, word)
      }
      else {
        quality_evaluation_df<-attribute_ranking(x, i, quality_evaluation_df, technical_aspect, word)
      }
    }
  }
  
  return(quality_evaluation_df)
}

first_iteration <- function(i) {
  if (i==1) {
    return(TRUE)
  }
  return(FALSE)
}

biological_condition <- function(x, i, quality_evaluation_df, condition, word) {
  idx<-which(x$lemma==word | x$token==word) #firstword
  if (length(idx)>0) { #if the word is present as lemma
    quality_evaluation_df[i,][[condition]]<-"Yes"
    # if (word=="size") {
    #   print(x[idx,]$sentence)
    # }
  }
  return(quality_evaluation_df)
}

biological_condition_split_word <- function(x, i, quality_evaluation_df, condition, word) {
  res<-cut_word(word)
  first_word<-res[1]
  second_word<-res[2]
  idx<-which(x$lemma==first_word | x$token==first_word) #firstword
  
  if (length(idx)>0) { #if the word is present as lemma
    for (id in idx) {   #if several times the word in the article
      if (x[(id+1),]$lemma==second_word | x[(id+1),]$token==second_word) {
        quality_evaluation_df[i,][[condition]]<-"Yes"
      }
    }
  }
  
  return(quality_evaluation_df)
}

biological_condition_double_space_word <- function(x, i, quality_evaluation_df, condition, word) {
  res<-cut_word(word)
  first_word<-res[1]
  second_word<-res[2]
  third_word<-res[3]
  idx<-which(x$lemma==first_word | x$token==first_word) #firstword
  
  if (length(idx)>0) { #if the word is present as lemma
    for (id in idx) {   #if several times the word in the article
      if (x[(id+1),]$lemma==second_word | x[(id+1),]$token==second_word) {
        if (x[(id+2),]$lemma==third_word | x[(id+2),]$token==third_word) {
          quality_evaluation_df[i,][[condition]]<-"Yes"
        }
      }
    }
  }
  
  return(quality_evaluation_df)
}

biological_condition_assessment <- function(x, i, pdf_name, quality_evaluation_df, ontology_in_vitro_in_vivo) {
  if (first_iteration(i)) {
    quality_evaluation_df$In_vitro<-"No"
    quality_evaluation_df$In_vivo<-"No"
  } else {
    quality_evaluation_df[i,]$In_vitro<-"No"
    quality_evaluation_df[i,]$In_vivo<-"No"
  }
  
  for (condition in names(ontology_in_vitro_in_vivo)) { 
    for (word in ontology_in_vitro_in_vivo[[condition]]) { 
      if (is_double_space(word)){
        quality_evaluation_df<-biological_condition_double_space_word(x, i, quality_evaluation_df, condition, word)
      }
      else if (is_space(word)) {
        quality_evaluation_df<-biological_condition_split_word(x, i, quality_evaluation_df, condition, word)
      }
      else if (is_not_space(word)){
        quality_evaluation_df<-biological_condition(x, i, quality_evaluation_df, condition, word)
      }
    }
  }
  
  return(quality_evaluation_df)
}

```

```{r}
run_assesment <- function(rds_list, ontology_material_characterisation, ontology_in_vitro_in_vivo) {
  i<-0
  quality_evaluation_df<-create_quality_df(ontology_material_characterisation)
  for (rds in rds_list) {
    i<-i+1
    x<-readRDS(file = paste0("~/Dev_pdf_poppler_output/", rds))
    pdf_name<-strsplit(rds, "/")[[1]][3]
    folder_name<-strsplit(rds, "/")[[1]][1]
    pdf_name<-str_replace_all(pdf_name, ".rds", "")
    quality_evaluation_df<-quality_assessment(x, i, pdf_name, quality_evaluation_df, ontology_material_characterisation, folder_name)
    quality_evaluation_df<-biological_condition_assessment(x, i, pdf_name, quality_evaluation_df, ontology_in_vitro_in_vivo) 
    if (first_iteration(i)) {
      quality_evaluation_df$Size_mm_section<-0 #size material and methods
    }
    quality_evaluation_df[i,]$Size_mm_section<-length(unique(x$sentence))
    }
  #compute the score
  quality_evaluation_df$Ranking<-rowSums(quality_evaluation_df[, names(ontology_material_characterisation)])
  return(quality_evaluation_df)
}

```


Below are the ontologies of terms used to rank the articles for the differents categories.

```{r ontologies, echo=TRUE}

#ontology of terms
ontology_material_characterisation <- list( Size = c("diameter", "size", "dimension", "radius", "nm"), 
                                   Surface_area = c("surface area"), 
                                   Surface_charge = c("zeta potential", "surface charge", "mv"),
                                   Chemical_composition = c("chemical composition", "coating", "core",
                                                            "shell", "content", "configuration", 
                                                            "molecular ratio"),
                                   # Concentration = c("final concentration", "dilution", "diluted", "mM"),
                                   Aggregation = c("aggregation", "aggregate", "polydisperse", "monodisperse",
                                                   "stability", "agglomeration", "stable", "agglomerate") #,
                                   # Wavelenght = c("wavelenght", "excitation wavelenght", "excitation", "emission",
                                   #                "emission wavelenght")
                                   )




ontology_in_vitro_in_vivo <- list( In_vitro = c("incubation temperature", "incubator", "incubated", "viability",
                                                "cells/ml", "cells/mL",  "cells/well", "cells per well", 
                                                "cultured", "culture", "medium", "media", "penicillin", "% of CO",
                                                "streptomycin", "well plates", "well plate", "cell line", "cells"), 
                                   
                                  In_vivo = c("age", "year old", "month old", "year-old", "month-old", 
                                              "cage", "holding rooms", "housed", "facility", "diet", "ad libitum",
                                              "dark cycle", "light cycle", "euthanized", "acclimate",
                                              "acclimatized", "body weight", "administration route", 
                                              "dose in mg/kg"))

```


```{r, , echo=TRUE}

rds_list<-list.files(path="~/Dev_pdf_poppler_output/", pattern = "\\.rds$", recursive=TRUE)

quality_evaluation_df<-create_quality_df(ontology_material_characterisation)

quality_evaluation_df<-run_assesment(rds_list, ontology_material_characterisation, ontology_in_vitro_in_vivo)
```


## Visualization of the Ranking :

This section shows the results of the automated ranking of the articles. The following plot show the number of articles for each ranking number :

```{r ranking, fig.height=10, fig.width=10, dpi=350, dev="jpeg"}
df <- quality_evaluation_df

df = within(df, {
  condition = ifelse((In_vitro == "Yes" & In_vivo == "Yes"), "Mixed", "Not_mixed")
})

p <- ggplot(df, aes(x=Ranking)) + geom_bar(fill="steelblue") +  geom_text(stat='count', aes(label=stat(count)), vjust=1.6, color="white") + theme_minimal() + scale_x_discrete(name ="Ranking",  limits=c(0,1,2, 3, 4, 5)) + ggtitle("Count of articles for each rank in the complete corpus") 
p
```

```{r}
data_excel<-  table(df$Ranking)

write.xlsx(data_excel, file = "quality_evaluation.xlsx", sheetName = "quality_evaluation", append = TRUE)
```


The following plot shows the ranking for the articles that has been automatically classified has containing in vivo experiments :

```{r }
p <- df %>% filter(In_vivo=="Yes") %>% ggplot(aes(x=Ranking)) + geom_bar(fill="steelblue") +
  geom_text(stat='count', aes(label=..count..), vjust=1.6, color="white") +
  theme_minimal() + ggtitle("Count of articles for each rank, \n for article classifed has inhas containing in vivo experiments") 
p
```

The following plot shows the ranking for the articles that has been automatically classified has containing in vitro experiments :

```{r }
p <- df %>% filter(In_vitro=="Yes") %>% ggplot(aes(x=Ranking)) + geom_bar(fill="steelblue") +
    geom_text(stat='count', aes(label=..count..), vjust=1.6, color="white") +
    theme_minimal() + ggtitle("Count of articles for each rank, \n for article classifed has inhas containing in vitro experiments") 
p
```

Finally, the following plot provide an estimation of the overall sizes of the material and methods section extracted. The unit is the number of sentences.

```{r }
p <- df  %>% ggplot(aes(x=Size_mm_section)) + geom_density(color="darkblue") + theme_minimal() + ggtitle("Size of the extracted \n Material and Method section, in sentences") 
p
```

Finally, here is a sample of best ranked articles :

```{r }
head(df[order(df$Ranking, decreasing = TRUE),], 30)
```
