---
title: "Validation quality"
author: "Etienne Rolland"
date: "19/02/2020"
output: 
  html_document :
    toc : true
  # github_document:
  #   toc: true
    
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Validation of the quality evaluation

This rmarkdown document report the quality evaluation performed on the pdf of the folder validation set (material and method extracted by the tool to segment article). The comparison is then plotted.


```{r include=FALSE}
library(dplyr)
library(readr)
library(stringr)
library(tabulizer)
library(tm)
library(ggplot2)
```

## Ranking of the material and method section

Note that the R code used to create the automatic ranking his hidded to make it more easily readable. A version with the code visible is available on the Github repository.



```{r functions}

create_quality_df <- function(material_characterisation) {
  #this function create the dataframe quality_evaluation that store the informations
  #of the quality evalution assessment
  
  #nb_technical_aspect<-length(material_characterisation)
  technical_aspect<-names(material_characterisation)
  names_columns<-c("Article_name", technical_aspect)
  names_columns<-c("Folder_name", technical_aspect)

  
  quality_evaluation_df<-as.data.frame(matrix(ncol=length(names_columns), 
                                              byrow=TRUE))
  
  colnames(quality_evaluation_df)<-names_columns
  
  return(quality_evaluation_df)
}

init_quality_df <- function(quality_evaluation_df, pdf_name, folder_name) {
  #create empty dataframe is such a pain in R
  #initiate the quality_df dataframe, i.e., add zero everywhere and the pdf name,
  #for the first iteration of the loop
  quality_evaluation_df[["Article_name"]]<-pdf_name
  quality_evaluation_df[["Folder_name"]]<-folder_name
  quality_evaluation_df[is.na(quality_evaluation_df)] = 0
  
  return(quality_evaluation_df)
}

is_double_space <- function(word) {
  res<-str_split(word, "\\s")[[1]]
  if (length(res)==3) {
    return(TRUE)
  }
  return(FALSE)
}

is_space <- function(word) {
  res<-str_split(word, "\\s")[[1]]
  if (length(res)==2) {
    return(TRUE)
  }
  return(FALSE)
}

is_not_space <- function(word) {
  res<-str_split(word, "\\s")[[1]]
  if (length(res)==1) {
    return(TRUE)
  }
  return(FALSE)
}

cut_word <- function(word) {
  res<-str_split(word, "\\s")[[1]]
  return(res)
}

attribute_ranking_split_word <- function(x, i, quality_evaluation_df, technical_aspect, word) {
  res<-cut_word(word)
  first_word<-res[1]
  second_word<-res[2]
  idx<-which(x$lemma==first_word) #firstword
  
  if (length(idx)>0) { #if the word is present as lemma
    for (id in idx) {   #if several times the word, simply
      if (x[(id+1),]$lemma==second_word) {
        quality_evaluation_df[i,][[technical_aspect]]<-1
      }
    }
  }
  
  return(quality_evaluation_df)
}

attribute_ranking <- function(x, i, quality_evaluation_df, technical_aspect, word) {
  idx<-which(x$lemma==word)
  if (length(idx)>0) { #if the word is present as lemma
    for (id in idx){
      sentence<-x[id,]$sentence
    }
    quality_evaluation_df[i,][[technical_aspect]]<-1
    # if (word=="size") {
    #   print(x[idx,]$sentence)
    # }
  }
  return(quality_evaluation_df)
}

quality_assessment <- function(x, i, pdf_name, quality_evaluation_df, ontology_material_characterisation, folder_name) {
  if (first_iteration(i)) {
    quality_evaluation_df<-init_quality_df(quality_evaluation_df, pdf_name, folder_name)
  } else {
    quality_evaluation_df<-rbind(quality_evaluation_df, c(0))
    quality_evaluation_df[i,]$Article_name<-pdf_name
    quality_evaluation_df[i,]$Folder_name<-folder_name
  }
  for (technical_aspect in names(ontology_material_characterisation)) { #Size, surface area, etc
    for (word in ontology_material_characterisation[[technical_aspect]]) { #Diameter
      if (is_space(word)) {
        quality_evaluation_df<-attribute_ranking_split_word(x, i, quality_evaluation_df, technical_aspect, word)
      }
      else {
        quality_evaluation_df<-attribute_ranking(x, i, quality_evaluation_df, technical_aspect, word)
      }
    }
  }
  
  return(quality_evaluation_df)
}

first_iteration <- function(i) {
  if (i==1) {
    return(TRUE)
  }
  return(FALSE)
}

biological_condition <- function(x, i, quality_evaluation_df, condition, word) {
  idx<-which(x$lemma==word | x$token==word) #firstword
  if (length(idx)>0) { #if the word is present as lemma
    quality_evaluation_df[i,][[condition]]<-"Yes"
    # if (word=="size") {
    #   print(x[idx,]$sentence)
    # }
  }
  return(quality_evaluation_df)
}

biological_condition_split_word <- function(x, i, quality_evaluation_df, condition, word) {
  res<-cut_word(word)
  first_word<-res[1]
  second_word<-res[2]
  idx<-which(x$lemma==first_word | x$token==first_word) #firstword
  
  if (length(idx)>0) { #if the word is present as lemma
    for (id in idx) {   #if several times the word in the article
      if (x[(id+1),]$lemma==second_word | x[(id+1),]$token==second_word) {
        quality_evaluation_df[i,][[condition]]<-"Yes"
      }
    }
  }
  
  return(quality_evaluation_df)
}

biological_condition_double_space_word <- function(x, i, quality_evaluation_df, condition, word) {
  res<-cut_word(word)
  first_word<-res[1]
  second_word<-res[2]
  third_word<-res[3]
  idx<-which(x$lemma==first_word | x$token==first_word) #firstword
  
  if (length(idx)>0) { #if the word is present as lemma
    for (id in idx) {   #if several times the word in the article
      if (x[(id+1),]$lemma==second_word | x[(id+1),]$token==second_word) {
        if (x[(id+2),]$lemma==third_word | x[(id+2),]$token==third_word) {
          quality_evaluation_df[i,][[condition]]<-"Yes"
        }
      }
    }
  }
  
  return(quality_evaluation_df)
}

biological_condition_assessment <- function(x, i, pdf_name, quality_evaluation_df, ontology_in_vitro_in_vivo) {
  if (first_iteration(i)) {
    quality_evaluation_df$In_vitro<-"No"
    quality_evaluation_df$In_vivo<-"No"
  } else {
    quality_evaluation_df[i,]$In_vitro<-"No"
    quality_evaluation_df[i,]$In_vivo<-"No"
  }
  
  for (condition in names(ontology_in_vitro_in_vivo)) { 
    for (word in ontology_in_vitro_in_vivo[[condition]]) { 
      if (is_double_space(word)){
        quality_evaluation_df<-biological_condition_double_space_word(x, i, quality_evaluation_df, condition, word)
      }
      else if (is_space(word)) {
        quality_evaluation_df<-biological_condition_split_word(x, i, quality_evaluation_df, condition, word)
      }
      else if (is_not_space(word)){
        quality_evaluation_df<-biological_condition(x, i, quality_evaluation_df, condition, word)
      }
    }
  }
  
  return(quality_evaluation_df)
}

```

```{r}
run_assesment <- function(rds_list, ontology_material_characterisation, ontology_in_vitro_in_vivo) {
  i<-0
  quality_evaluation_df<-create_quality_df(ontology_material_characterisation)
  for (rds in rds_list) {
    i<-i+1
    x<-readRDS(file = paste0("~/Validation/", rds))
    pdf_name<-strsplit(rds, "/")[[1]][2]
    folder_name<-strsplit(rds, "/")[[1]][1]
    pdf_name<-str_replace_all(pdf_name, ".rds", "")
    quality_evaluation_df<-quality_assessment(x, i, pdf_name, quality_evaluation_df, ontology_material_characterisation, folder_name)
    quality_evaluation_df<-biological_condition_assessment(x, i, pdf_name, quality_evaluation_df, ontology_in_vitro_in_vivo) 
    if (first_iteration(i)) {
      quality_evaluation_df$Size_mm_section<-0 #size material and methods
    }
    quality_evaluation_df[i,]$Size_mm_section<-length(unique(x$sentence))
    }
  #compute the score
  quality_evaluation_df$Ranking<-rowSums(quality_evaluation_df[, names(ontology_material_characterisation)])
  return(quality_evaluation_df)
}

```


Below are the ontologies of terms used to rank the articles for the differents categories.

```{r ontologies, echo=TRUE}

#ontology of terms
ontology_material_characterisation <- list( Size = c("diameter", "size", "dimension", "radius", "nm"), 
                                   Surface_area = c("surface area"), 
                                   Surface_charge = c("zeta potential", "surface charge", "mv"),
                                   Chemical_composition = c("chemical composition", "coating", "core",
                                                            "shell", "content", "configuration", 
                                                            "molecular ratio"),
                                   # Concentration = c("final concentration", "dilution", "diluted", "mM"),
                                   Aggregation = c("aggregation", "aggregate", "polydisperse", "monodisperse",
                                                   "stability", "agglomeration", "stable", "agglomerate") #,
                                   # Wavelenght = c("wavelenght", "excitation wavelenght", "excitation", "emission",
                                   #                "emission wavelenght")
                                   )




ontology_in_vitro_in_vivo <- list( In_vitro = c("incubation temperature", "incubator", "incubated", "viability",
                                                "cells/ml", "cells/mL",  "cells/well", "cells per well", 
                                                "cultured", "culture", "medium", "media", "penicillin", "% of CO",
                                                "streptomycin", "well plates", "well plate", "cell line", "cells"), 
                                   
                                  In_vivo = c("age", "year old", "month old", "year-old", "month-old", 
                                              "cage", "holding rooms", "housed", "facility", "diet", "ad libitum",
                                              "dark cycle", "light cycle", "euthanized", "acclimate",
                                              "acclimatized", "body weight", "administration route", 
                                              "dose in mg/kg"))

```


```{r, , echo=TRUE}

rds_list<-list.files(path="~/Validation", pattern = "\\.rds$", recursive=TRUE)

quality_evaluation_df<-create_quality_df(ontology_material_characterisation)

quality_evaluation_df<-run_assesment(rds_list, ontology_material_characterisation, ontology_in_vitro_in_vivo)
```

## Vizualisation of the results

```{r}
df <- quality_evaluation_df

p <- df  %>% ggplot(aes(x=Size_mm_section)) + geom_density(color="darkblue") + theme_minimal() + ggtitle("Size of the extracted \n Material and Method section, in sentences") 
p
```

```{r}
articles<-c("Ansari, M 2018.pdf",
"Bai, K J et al 2018.pdf",
"Blum, J L et al 2014.pdf",
"Chen et al 2008.pdf",
"Jamshidzadeh, A et al 2015.pdf",
"Li, C et al 2009.pdf",
"Li, J et al 2013.pdf",
"Li, J G et al 2009.pdf",
"Li, Y et al 2010.pdf",
"Liu, Y et al 2014.pdf",
"Love, S A et al 2012.pdf",
"Maurizi, L et al 2015.pdf",
"Nešković, O et al 2013.pdf",
"Neun, B W et al 2018.pdf",
"Reddy, A et al 2010.pdf",
"Richter, AW et al 1983.pdf",
"Sadaf, A et al 2012.pdf",
"Tang, J et al 2009.pdf",
"Vicente, S et al 2017.pdf",
"Wang, X et al 2010.pdf",
"Xiaoli, F et al 2017.pdf",
"Yan, M et al 2011.pdf",
"Yu, T et al 2011.pdf",
"Zook, J M et al 2011.pdf",
"Abbasalipourkabir R et al 2015.pdf",
"Abe, S et al 2012.pdf",
"Adedara, I A et al 2018.pdf",
"Aijie, C et al 2017.pdf",
"Amrollahi-Sharifabadi et al. 2018.pdf",
"Aragao-Santiago, L 2016.pdf",
"AshaRani et al. 2009.pdf",
"Bendre, V et al 2011.pdf",
"Cabral, H et al 2005.pdf")

ranks<-c(2,
3,
1,
2,
2,
0,
1,
0,
0,
2,
3,
3,
0,
0,
2,
0,
1,
1,
2,
2,
2,
2,
3,
2,
0,
0,
3,
4,
3,
2,
0,
0,
2)

```

```{r}
data <- data.frame("Articles" = articles, "Manual_ranking" = ranks)
data <- data %>% filter(Articles %in% quality_evaluation_df$Article_name)
data <- data[order(data$Articles),]
quality_evaluation_df<-quality_evaluation_df %>% filter(Article_name %in% articles)
quality_evaluation_df <- quality_evaluation_df [order(quality_evaluation_df$Article_name),]
data$Automatic_ranking<-quality_evaluation_df$Ranking
```



