---
title: "Validation of the tool"
author: "Etienne Rolland"
date: "20/04/2020"
output: 
  # html_document :
  #   toc : true
  github_document:
    toc: true
    
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Checking the corpus of validation

```{r}
library(segmenteR)
library(udpipe)
```

```{r}
setwd("~/Bureau")
validation_set<-list.files("Validation Set/")
```

```{r}
articles<-c("Ansari, M 2018.pdf",
"Bai, K J et al 2018.pdf",
"Blum, J L et al 2014.pdf",
"Chen et al 2008.pdf",
"Jamshidzadeh, A et al 2015.pdf",
"Li, C et al 2009.pdf",
"Li, J et al 2013.pdf",
"Li, J G et al 2009.pdf",
"Li, Y et al 2010.pdf",
"Liu, Y et al 2014.pdf",
"Love, S A et al 2012.pdf",
"Maurizi, L et al 2015.pdf",
"Nešković, O et al 2013.pdf",
"Neun, B W et al 2018.pdf",
"Reddy, A et al 2010.pdf",
"Richter, AW et al 1983.pdf",
"Sadaf, A et al 2012.pdf",
"Tang, J et al 2009.pdf",
"Vicente, S et al 2017.pdf",
"Wang, X et al 2010.pdf",
"Xiaoli, F et al 2017.pdf",
"Yan, M et al 2011.pdf",
"Yu, T et al 2011.pdf",
"Zook, J M et al 2011.pdf",
"Abbasalipourkabir R et al 2015.pdf",
"Abe, S et al 2012.pdf",
"Adedara, I A et al 2018.pdf",
"Aijie, C et al 2017.pdf",
"Amrollahi-Sharifabadi et al. 2018.pdf",
"Aragao-Santiago, L 2016.pdf",
"AshaRani et al. 2009.pdf",
"Bendre, V et al 2011.pdf",
"Cabral, H et al 2005.pdf")
```

```{r}
table(articles %in% validation_set)
table(validation_set %in% articles)
```
```{r}
articles[which(articles %in% validation_set)]
```

```{r}
articles[which(!articles %in% validation_set)]
```
The three missing articles, 
[1] "Amrollahi-Sharifabadi et al. 2018.pdf" "Aragao-Santiago, L 2016.pdf"           "Cabral, H et al 2005.pdf"             
Has been downloaded in the 20 April of 2021.
They were absent from the repository in pdf.

This may explain why the double box plot only contains 28 points, where the manual ranking contain 33 articles. 3 were missing.

```{r}
list.files("Missing_validation_set/")
```

```{r}
validation_set<-list.files("Validation_set_combined//")
articles[which(!articles %in% validation_set)]
table(articles %in% validation_set)
```
## Third folder to managed more easily the manual reading of the article in pdf

```{r}
articles_to_clean <- list.files("Validation_tool_folder/")
for (article in articles_to_clean) {
  print(article)
  file.remove(paste0("Validation_tool_folder/", article))
}
print("After cleaning :")
list.files("Validation_tool_folder/")
```



```{r}
#Validation_tool_folder
length(articles)
for (article in articles) {
  print(article)
  file.copy(paste0("Validation_set_combined/", article), paste0("Validation_tool_folder/", article))
}
```

```{r}
length(list.files("Validation_tool_folder/"))
list.files("Validation_tool_folder/")
```


# Extraction of the materials and methods and results sections for comparison

## Automatic extraction via segmenteR

```{r}
## udpipe got the model for annotation
dl <- udpipe::udpipe_download_model("english-gum")
str(dl)
```

```{r}
model <- udpipe_load_model(file = dl$file_model)
model
```
```{r}
library(stringr)
```


```{r}
for (article in articles) {
  #do segmentation
  #from manual extraction :
  #path = paste0("Validation_tool_folder/", pdf_name)
  print(article)
  path = paste0("Validation_tool_folder/", article)
  section_aliases <- c("material", "method", "experimental", "experiment", "methodology")

  #model definition can be skipped, the function can download it automatically
  material_and_methods <- data.frame()
  material_and_methods <- try(segmenteR::extract_section_from_pdf(pdf_name=path,
                                                             udpipe_model=model, 
                                                             section_aliases=section_aliases))
  saveRDS(material_and_methods, file=paste0("Validation_tool_folder/segmenteR_", article, ".rds"))

}
```


## Manual extraction

### Functions

```{r}
pdf_name<-"Cabral, H et al 2005.pdf"
```

```{r}
#function to open the article passed as input and preprocess
open_pdf_and_annotate <- function(pdf_name, model) {
  
  #open the pdf so the user can read it
  
  path = paste0("Validation_tool_folder/", pdf_name)
  fs::file_show(path)
  
  remove_bibliography <- TRUE

  txt_pdf <- tabulizer::extract_text(path) # read the text from the pdf
  txt_pdf <- segmenteR::preprocess_article_txt(txt_pdf)
  conllu_df <- segmenteR::annotate_txt_pdf(txt_pdf, udpipe_model=model ) # create the dataframe for NLP using udpipe
  
  return(conllu_df)
}

```

```{r}
conllu_df<-open_pdf_and_annotate(pdf_name, model)
```

```{r}
head(conllu_df)
```

```{r}
word <- "Materials"

display_occurences <- function(word, conllu_df) {
  idx<-which(conllu_df$token==word)
  print(idx)
  conllu_df[idx,]$sentence
}

display_occurences(word, conllu_df)
```
```{r}
display_occurences("570", conllu_df)

```


```{r}
cut_conllu_df <- function(idx1, idx2, conllu_df) {
  
  section <- conllu_df[idx1:idx2,]
  print(unique(section$sentence))
  return(section)
  
}
```


```{r}
res<-cut_conllu_df(1504, 2628, conllu_df)
```

```{r}
head(res)
```

```{r}
#save RDS file
pdf_name
saveRDS(res, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))
```

### Extraction of the materials and methods section

One block for each article :

```{r}
pdf_name <- "Ansari, M 2018.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "Materials"
word_end_mm <- "CA"

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(846, 1852, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

```{r}
pdf_name <- "Bai, K J et al 2018.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "Methods"
word_end_mm <- "05"

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(1639, 3893, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

```{r}
pdf_name <- "Blum, J L et al 2014.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "Materials"
word_end_mm <- "05" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(1674, 3478, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

```{r}
pdf_name <- "Chen et al 2008.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "Materials"
word_end_mm <- "conditions" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(952, 2414, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

```{r}
pdf_name <- "Jamshidzadeh, A et al 2015.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "MATERIALS"
word_end_mm <- "05" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(918, 1541, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

```{r}
pdf_name <- "Li, C et al 2009.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "Materials"
word_end_mm <- "t-test" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(3161, 5965, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

```{r}
pdf_name <- "Li, J et al 2013.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "2."
word_end_mm <- "05" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(1044, 2693, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

Following article have a material and method section starting by EXPERIMENTAL.

```{r}
pdf_name <- "Li, J G et al 2009.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "EXPERIMENTAL"
word_end_mm <- "microscopy" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(493, 1212, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

```{r}
pdf_name <- "Li, Y et al 2010.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "MATERIALS"
word_end_mm <- "microscopy" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(895, 1475, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

```{r}
pdf_name <- "Liu, Y et al 2014.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "Materials"
word_end_mm <- "significant" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(1314, 3601, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

Love, S A et al 2012.pdf : no real material and method section
```{r}
pdf_name <- "Love, S A et al 2012.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "Nanoparticle"
word_end_mm <- "USA" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(1272, 3021, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```


```{r}
pdf_name <- "Maurizi, L et al 2015.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "MATERIALS"
word_end_mm <- "t-test" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(1311, 3877, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

Nešković, O et al 2013.pdf : book chapter

```{r}
pdf_name <- "Nešković, O et al 2013.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "Materials"
word_end_mm <- "ImageJ." 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(1231, 3005, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

Neun, B W et al 2018.pdf : book chapter

```{r}
pdf_name <- "Neun, B W et al 2018.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "Materials"
word_end_mm <- "Doxil" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(1283, 3125, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

```{r}
pdf_name <- "Neun, B W et al 2018.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "Materials"
word_end_mm <- "Doxil" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(1283, 3125, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

```{r}
pdf_name <- "Reddy, A et al 2010.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "Materials"
word_end_mm <- "significant" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(1395, 2922, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

"Richter, AW et al 1983.pdf" : it is a scan. 1983.

```{r}
pdf_name <- "Richter, AW et al 1983.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "Materials"
word_end_mm <- "significant" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(1395, 2922, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

```{r}
pdf_name <- "Sadaf, A et al 2012.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "MATERIALS"
word_end_mm <- "05" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(889, 2155, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

```{r}
pdf_name <- "Tang, J et al 2009.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "MATERIALS"
word_end_mm <- "significant" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(637, 1354, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

```{r}
pdf_name <- "Vicente, S et al 2017.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "METHODS"
word_end_mm <- "USA" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(1235, 2601, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

```{r}
pdf_name <- "Wang, X et al 2010.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "MATERIALS"
word_end_mm <- "05" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(1412, 2622, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

```{r}
pdf_name <- "Xiaoli, F et al 2017.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "Materials"
word_end_mm <- "significant" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(53, 4366, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

```{r}
pdf_name <- "Yan, M et al 2011.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "Materials"
word_end_mm <- "test" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(1713, 4188, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

```{r}
pdf_name <- "Yu, T et al 2011.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "METHODS"
word_end_mm <- "software" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(7273, 9242, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

```{r}
pdf_name <- "Zook, J M et al 2011.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "Materials"
word_end_mm <- "centrifugation" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(1739, 4790, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```


```{r}
pdf_name <- "Abbasalipourkabir R et al 2015.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "Materials"
word_end_mm <- "less" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(1061, 2339, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

```{r}
pdf_name <- "Abe, S et al 2012.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "EXPERIMENTAL"
word_end_mm <- "Ref" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(1127, 1701, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```


```{r}
pdf_name <- "Adedara, I A et al 2018.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "Materials"
word_end_mm <- "significant" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(1055, 2583, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

```{r}
pdf_name <- "Aijie, C et al 2017.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "Material"
word_end_mm <- "significant" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(1280, 3030, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

```{r}
pdf_name <- "Amrollahi-Sharifabadi et al. 2018.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "Materials"
word_end_mm <- "USA" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(1790, 3112, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

```{r}
pdf_name <- "Aragao-Santiago, L 2016.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "Methods"
word_end_mm <- "lower" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(1113, 3548, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

```{r}
pdf_name <- "AshaRani et al. 2009.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "MATERIALS"
word_end_mm <- "Internet" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(7422, 10247, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```

```{r}
pdf_name <- "Bendre, V et al 2011.pdf"
conllu_df<-open_pdf_and_annotate(pdf_name, model)

word_start_mm <- "MATERIALS"
word_end_mm <- "required" 

display_occurences(word_start_mm, conllu_df)
display_occurences(word_end_mm, conllu_df)

mm_section<-cut_conllu_df(574, 980, conllu_df)
saveRDS(mm_section, file=paste0("Validation_tool_folder/", pdf_name, ".rds"))

```








# Benchmach and performance of the tool

```{r}
all_sections <-list.files("Validation_tool_folder/", pattern = ".rds")
all_sections
```

```{r}
automatic_extraction<-list.files("Validation_tool_folder/", pattern = "segmenteR")
automatic_extraction
```
```{r}
manual_extraction<-all_sections[!all_sections %in% automatic_extraction]
```

```{r}
benchmarck_df <- data.frame(manual_extraction, automatic_extraction)
benchmarck_df
```

Function from this package [this package]https://rdrr.io/cran/qlcMatrix/man/sim.strings.html). More easy to compute than creating a dtm on the whole corpus (i.e., all the material and sections.)

```{r}
#function to got the cosine similarity
library(qlcMatrix)
Manual<-readRDS("Validation_tool_folder/Abbasalipourkabir R et al 2015.pdf.rds")
Auto<-readRDS("Validation_tool_folder/segmenteR_Abbasalipourkabir R et al 2015.pdf.rds")
```

```{r}
Manual_sentences<-unique(Manual$sentence)
Manual_sentences<-paste0(Manual_sentences, collapse = " ")
Manual_sentences
```

```{r}
Auto_sentences<-unique(Auto$sentence)
Auto_sentences<-paste0(Auto_sentences, collapse = " ")
Auto_sentences
```


```{r}
qlcMatrix::sim.strings(Manual_sentences, Auto_sentences)
```
```{r}
got_cosine_similiarty <- function(benchmarck_df_row) {
  
  Manual<-readRDS(paste0("Validation_tool_folder/", benchmarck_df_row$manual_extraction))
  Auto<-readRDS(paste0("Validation_tool_folder/", benchmarck_df_row$automatic_extraction))
  
  Manual_sentences<-unique(Manual$sentence)
  Manual_sentences<-paste0(Manual_sentences, collapse = " ")

  Auto_sentences<-unique(Auto$sentence)
  Auto_sentences<-paste0(Auto_sentences, collapse = " ")

  cosine_similarity <- qlcMatrix::sim.strings(Manual_sentences, Auto_sentences)
  return(cosine_similarity)
}
```

```{r}
benchmarck_df$cosine_similarity <- 0
head(benchmarck_df)
```
```{r}
for (i in 1:33) {
  print(i)
  if (i == 10 |i == 25) {
    print(benchmarck_df[i,]$manual_extraction)
    print("Error")
    #to remove the error message in the benchmarck df due to the failure of try()
    benchmarck_df[i,]$cosine_similarity <- 0
    next

  }
  cosine_sim <-try(got_cosine_similiarty(benchmarck_df[i,]))
  benchmarck_df[i,]$cosine_similarity <- cosine_sim
} 
```


```{r}
benchmarck_df
```


### What about the two articles on which it fails ?

Running the code line by line, on Bendre, V et al 2011.pdf, it appears that clean_title_journal(pdf_name, section_title_df) remove all section title because the article only does 2 pages.

Richter, AW et al 1983.pdf is a pdf, but a pdf of a scan, and has no information regarding or, well, text.